### 2019-08-23 README.Rmd
Clarification in README introduction

The goal of diffEnrich is simple. Given a list of gene symbols, *diffEnrich*  will
perform differential enrichment analysis using the Kyoto Encyclopedia of Genes
and Genomes (KEGG) REST API. This package provides a number of functions that are 
intended to be used in a pipeline (See Figure N). Briefly, the workflow will
download and clean species specific ENTREZ gene IDs and map them to their respective
KEGG pathways by accessing KEGG's REST API. This way the user will always have 
the most up-to-date pathway data from KEGG. Next, the user will identify significantly
enriched pathways from two different gene sets, and finally, the user will identify 
pathways that are differentially expressed between the two gene sets. In addition to 
the analysis pipeline, this package also provides functions for data visualizations.

>>>>

The goal of diffEnrich is simple. Given a list of gene symbols, *diffEnrich*  will
perform differential enrichment analysis using the Kyoto Encyclopedia of Genes
and Genomes (KEGG) REST API. This package provides a number of functions that are 
intended to be used in a pipeline (See Figure N). Briefly, the workflow will
download and clean species specific ENTREZ gene IDs and map them to their respective
KEGG pathways by accessing KEGG's REST API. This way the user will always have 
the most up-to-date pathway data from KEGG. Next, the user will identify significantly
enriched pathways from two different gene sets, and finally, the user will identify 
pathways that are differentially enriched between the two gene sets. In addition to 
the analysis pipeline, this package also provides a plotting function.
